\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-11-28 Final Paper/PaperJLin.tex
Added comments for corrections

\section{Introduction}

@@

@@

% Table for D1015 - election type
\begin{table}
	\centering
	%\resizebox{\columnwidth}{!}
	%\def\arraystretch{1.5}
	\caption{\tb{Types of Election by Polity}}
	\begin{tabulary}{\textwidth}{l c c c c} 
		\hline
		\tb{Country}&\tb{Year}&\tb{Legislative}&\tb{Both}&\tb{Presidential}\\
		\hline
		Argentina&2015&-&X&-\\
		Australia&2013&X&-&-\\
		Austria&2013&X&-&-\\
		Bulgaria&2014&X&-&-\\
		Czech Republic&2013&X&-&-\\
		Finland&2015&X&-&-\\
		France&2012&-&-&X\\
		Germany&2013&X&-&-\\ 
		Great Britain&2015&X&-&-\\
		Greece&2012/2015&X&-&-\\
		Iceland&2013&X&-&-\\
		Ireland&2011&X&-&-\\
		Israel&2013&X&-&-\\
		Japan&2013&X&-&-\\
		Kenya&2013&-&X&-\\
		Latvia&2011/2014&X&-&-\\
		Mexico&2012&-&X&-\\
		Mexico&2015&X&-&-\\
		Montenegro&2012&X&-&-\\
		Norway&2013&X&-&-\\
		New Zealand&2011/2014&X&-&-\\
		Peru&2016&-&X&-\\
		Philippines&2016&-&X&-\\
		Poland&2011&X&-&-\\
		Portugal&2015&X&-&-\\	
		Romania&2012&X&-&-\\
		Romania&2014&-&-&X\\
		Serbia&2012&-&X&-\\
		Slovakia&2016&X&-&-\\
		Slovenia&2011&X&-&-\\
		South Africa&2014&X&-&-\\ 
		South Korea&2012&X&-&-\\
		Sweden&2014&X&-&-\\
		Switzerland&2011&X&-&-\\
		Turkey&2015&X&-&-\\
		\hline
	\end{tabulary} \\
	\e{Source:} Comparative Study of Electoral Systems Module IV 
	\label{table1}
\end{table}

@@

Table \ref{table1} shows the types of elections that are held within each of the polities that are represented in the Comparative Study of Electoral Systems Module IV data. From this table, we see that many of the countries are holding legislative, or parliamentary elections to some extent during the period between 2011 and 2016. This table provides some background for the context in each of the polities that will be included in the analysis.

@@

%Thailand&76.24&3.61&4.08&16.07 \\
Figure \ref{figure1} provides a general overview of the place of residence of the respondents for the data used in this study. At an instant glance, it may appear that the urban residents are oversampled, but considering that, as Table \ref{table2} suggests, more people live in urban centers than suburban areas, it balances out to represent the world's populations on a general trend.

\begin{figure}[ht!]    \centering
	{	 \includegraphics[width=\textwidth]{Residents}}
	\caption{\tb{Distribution of Responses By Place of Residence}}\label{figure1}
\end{figure}

@@

>>>>

%\section{Introduction}

@@

%%%TEASE out this section a bit more to add the explaination for why diversity in urban centers would make it more likely for them to be more liberal.

@@

% Table for D1015 - election type
%\begin{table}
%	\centering
	%\resizebox{\columnwidth}{!}
	%\def\arraystretch{1.5}
%	\caption{\tb{Types of Election by Polity}}
%	\begin{tabulary}{\textwidth}{l c c c c} 
%		\hline
%		\tb{Country}&\tb{Year}&\tb{Legislative}&\tb{Both}&\tb{Presidential}\\
%		\hline
%		Argentina&2015&-&X&-\\
%		Australia&2013&X&-&-\\
%		Austria&2013&X&-&-\\
%		Bulgaria&2014&X&-&-\\
%		Czech Republic&2013&X&-&-\\
%		Finland&2015&X&-&-\\
%		France&2012&-&-&X\\
%		Germany&2013&X&-&-\\ 
%		Great Britain&2015&X&-&-\\
%		Greece&2012/2015&X&-&-\\
%		Iceland&2013&X&-&-\\
%		Ireland&2011&X&-&-\\
%		Israel&2013&X&-&-\\
%		Japan&2013&X&-&-\\
%		Kenya&2013&-&X&-\\
%		Latvia&2011/2014&X&-&-\\
%		Mexico&2012&-&X&-\\
%		Mexico&2015&X&-&-\\
%		Montenegro&2012&X&-&-\\
%		Norway&2013&X&-&-\\
%		New Zealand&2011/2014&X&-&-\\
%		Peru&2016&-&X&-\\
%		Philippines&2016&-&X&-\\
%		Poland&2011&X&-&-\\
%		Portugal&2015&X&-&-\\	
%		Romania&2012&X&-&-\\
%		Romania&2014&-&-&X\\
%		Serbia&2012&-&X&-\\
%		Slovakia&2016&X&-&-\\
%		Slovenia&2011&X&-&-\\
%		South Africa&2014&X&-&-\\ 
%		South Korea&2012&X&-&-\\
%		Sweden&2014&X&-&-\\
%		Switzerland&2011&X&-&-\\
%		Turkey&2015&X&-&-\\
%		\hline
%	\end{tabulary} \\
%	\e{Source:} Comparative Study of Electoral Systems Module IV 
%	\label{table1}
%\end{table}

@@

%Table \ref{table1} shows the types of elections that are held within each of the polities that are represented in the Comparative Study of Electoral Systems Module IV data. From this table, we see that many of the countries are holding legislative, or parliamentary elections to some extent during the period between 2011 and 2016. This table provides some background for the context in each of the polities that will be included in the analysis.

@@

%Thailand&76.24&3.61&4.08&16.07 \\
% Figure \ref{figure1} provides a general overview of the place of residence of the respondents for the data used in this study. At an instant glance, it may appear that the urban residents are oversampled, but considering that, as Table \ref{table2} suggests, more people live in urban centers than suburban areas, it balances out to represent the world's populations on a general trend.

%\begin{figure}[ht!]    \centering
%	{	 \includegraphics[width=\textwidth]{Residents}}
%	\caption{\tb{Distribution of Responses By Place of Residence}}\label{figure1}
%\end{figure}

@@

%Add controls for Gender (D2002) , Age (2018-D2001_Y) and Socioeconomic status (D2012)
